A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
discussed the klages-mundt paper

\and
\IEEEauthorblockN{Markus Fix}
\IEEEauthorblockA{\textit{Keep Network} \\
markus@keep.network}

\and
\IEEEauthorblockN{Liam Zebedee}
\IEEEauthorblockA{\textit{Keep Network} \\
liam@keep.network}
}

@@

\section{Analysis of Token based systems}

Discuss the use of ABM for token engineering. Cite recent papers.

@@

\textit{Percent Lynchpinned Signatures}

>>>>

\and
\IEEEauthorblockN{Markus Fix}
\IEEEauthorblockA{\textit{Keep Network} \\
markus@keep.network}
}

@@

\section{Analysis of Token based systems}
Klages-Mundt et al.\cite{klages2019stability} use agent based models to simulate a decentralized stable coin
system and shows how deleveraging sprial attacks could occur. Their model is also able
to explain real complex stable coin movements. Further, the study is able
to show theoretically that regions of stability and instability exist for such decentralized
stable coin systems.

While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to

@@

\textit{Percent Lynchpinned Signatures} Why does this not fluctuate as much?
